---
title: "A UN Report on the Relationship between GDP and Life Expectancy"
author: "_Your Name Here_"
date: _Today's date_
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r packages, include=FALSE}
library(tidyverse) ##contains ggplot package
```

# Introduction

This report was prepared to the attention of the United Nations. It analyzes the relationship between a country's GDP, its life expectancy and CO2 emissions. Our goal is to determine to what degree a country’s economic strength or weakness may be related to its public health status and impact on climate pollution. We hypothesize that both life expectancy and CO2 emissions increase with a country's GDP.

```{r data, include=FALSE}
gapminder_1997 <- read_csv("../data/gapminder_1997.csv")
```

# My plot 

```{r gdp_lifeexp_1997, echo=TRUE}
ggplot(data=gapminder_1997) + aes(x = gdpPercap, y = lifeExp,
                                  color = continent) +
  geom_point() + labs(x = "GDP per capita", y = "Life Expectancy",
                      title = "GPD per capita vs. Life Expectancy in 1997")
```

```{r data_summary, include=TRUE}
nCountries <- gapminder_1997 %>%
  select(country) %>% 
  n_distinct()
```

The number of countries that entered the above analysis was `r nCountries`.  


1. **R**
1. *ggplot*
1. ***automating RMarkdown files from the command line***
1. [An RMarkdown Cheat Sheet](https://rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf)